Joint Power Allocation and Network Slicing in an End-to-End ORAN System \vspace{-.1cm}

### 2019-10-28 Latex/tex/pr.tex
submit version1

Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},$ and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}$, respectively.

>>>>

Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
